Updates on the Exoplanet Orbit Database

### 2014-03-06 draft/ms.tex
Partial re-aranging of table.

\begin{deluxetable}{llll}
\tabletypesize{\scriptsize}
%\rotate
\tablewidth{0pt}
\tablecaption{Fields of Exoplanet Orbit Database\label{tab:par}}
\tablehead{
  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{b}}
}
\startdata

@@

NAME\dotfill & String & Name of planet & \nodata \\
OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\

@@

KEPID\dotfill & Long Integer & The unique \kepler\ star identifier & \nodata \\
KOI\dotfill & Float & KOI object number & \nodata \\
KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\

@@

PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
FIRSTREF\dotfill & String & First peer-reviewed publication of
planetary orbit & FIRSTURL \\
ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
\sidehead{\textbf{Stellar Properties}}
STAR\dotfill & String & Standard name for host star & \nodata \\
MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\
LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
host star in cgs unit & -UPPER, etc. \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\
\sidehead{\textbf{Links}}
JSNAME\dotfill & String & Name of host star used in the Extrasolar
Planets Encyclopaedia & EPEURL \\
ETDNAME\dotfill & String & Name of planet used in the Exoplanet
Transit Database & ETDURL \\
SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
planet, if available) & SIMBADURL \\
EANAME\dotfill & String & Name of planet used in the Exoplanet
Archive database & EAURL \\
\enddata
\tablenotetext{a}{Fields in bold are updates or new additions from
  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
where ``-" stands for the name of the field listed in the first
column. They are...}
\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};
  changed to other commonly used name for planet.}
\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
  still not consistent.}
\end{deluxetable}

>>>>

% NEW ORGANIZATION ACCORDING TO INDIVIDUAL PLANET PAGE
\begin{deluxetable}{llll}
\tabletypesize{\scriptsize}
%\rotate
\tablewidth{0pt}
\tablecaption{Fields of Exoplanet Orbit Database\label{tab:par}}
\tablehead{
  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{b}}
}
\startdata
%
\sidehead{\textbf{Discovery and References}}
NAME\dotfill & String & Name of planet & \nodata \\
OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
FIRSTREF\dotfill & String & First peer-reviewed publication of
planetary orbit & FIRSTURL \\
JSNAME\dotfill & String & Name of host star used in the Extrasolar
Planets Encyclopaedia & EPEURL \\
ETDNAME\dotfill & String & Name of planet used in the Exoplanet
Transit Database & ETDURL \\
EANAME\dotfill & String & Name of planet used in the Exoplanet
Archive database & EAURL \\
SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
planet, if available) & SIMBADURL \\
KEPID\dotfill & Long Integer & The unique \kepler\ star identifier &
\nodata \\
KOI\dotfill & Float & KOI object number & \nodata \\
KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\

% STILL OLD SORTING BELOW

@@

@@

@@

%
\sidehead{\textbf{Stellar Properties}}
STAR\dotfill & String & Standard name for host star & \nodata \\
MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\
LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
host star in cgs unit & -UPPER, etc. \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\
%
\sidehead{\textbf{Links}}

\enddata
\tablenotetext{a}{Fields in bold are updates or new additions from
  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
where ``-" stands for the name of the field listed in the first
column. They are...}
\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};
  changed to other commonly used name for planet.}
\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
  still not consistent.}
\end{deluxetable}
